### 2019-10-31 inst/README.rmd
adds new README example and text

```{r eval = TRUE, echo = FALSE results = "hide"}
library(CodeDepends)
script <- system.file(
    "example", 
    "simple_script.R", 
    package = "Rclean")

@@

Sometimes for more complicated scripts, it can be helpful to see a
 network graph showing the interdependencies of
 variables. `code_graph` will produce a network diagram showing which
 lines of code produce which variables (e.g. 1 -> "out"):

@@

Now, we can now pick the result we want to focus on for cleaning:

@@

>>>>

```{r eval = TRUE, echo = FALSE, results = "hide"}
library(CodeDepends)
script <- system.file(
    "example", 
    "simple_script.R", 
    package = "Rclean")

@@

Sometimes for more complicated scripts, it can be helpful to see a
 network graph showing the interdependencies of
 variables. `code_graph` will produce a network diagram showing which
 lines of code produce or use which variables (e.g. 1 -> "out"):

@@

Now, we can pick the result we want to focus on for cleaning:

@@

This is an open-source project. If you would like to contribute to the
project, please check out [CONTRIBUTING.md](CONTRIBUTING.md).
